Level-Set method on \texttt{p4est}

### 2014-09-03 paper/tex/introduction.tex
updated introduction and added refs (see details)
currently newer refs are added in the refs.bib until we finialize on
which ones we actually want to retain. For the older ones we use the
master ref for CASL.

To cope with the fact that the file could be in different locations on
different machines, please add a symlink casl.bib to point to the actual
reference file on you machine. This file was not added to the repo since
the address could be different.

A better approach is to put the reference file in a system-provided
location that can be accessed by latex without the need for any relative

\item \textbf{Parallel semi-lagrangian methods? What are the challenges? Whats out there?}
Parallel level-set algorithms can be categorized in three separate groups: 1) Parallel advection algorithms, 2) Parallel reinitialization algorithms, and 3) Parallel motion under curvature algorithms. In this article we focus on developing algorithms for the first two categories. We also make use of the popular \texttt{PETSc} \fcite{petsc} library for solution of the linear systems that arise from the third category. Moreover, \texttt{PETSc} provides primitives, such as parallel ghosted vector and scatter/gather operations, which simplifies the implementation.

@@

\item \textbf{Parallel reinitialization methods? What are the challenges? Whats out there?}

>>>>

\item \textbf{Parallel advection methods? What are the challenges?}
Parallel level-set algorithms can be categorized in three separate groups: 1) Parallel advection algorithms, 2) Parallel reinitialization algorithms, and 3) Parallel motion under curvature algorithms. In this article we focus on developing algorithms for the first two categories. We also make use of the popular \texttt{PETSc} \fcite{petsc} library for solution of the linear systems that arise from the third category. Moreover, \texttt{PETSc} provides primitives, such as parallel ghosted vector and scatter/gather operations, which simplifies the implementation.

@@

\item \textbf{Parallel reinitialization methods? What are the challenges?}
In several applications of the level-set method, it is desirable for the level-set function to be a signed distance function, i.e. $|\nabla \phi| = 1$. There are generally two approaches to enforce this property: 1) Solving the pseudo-time transient reinitialization equation $\phi_\tau + S(\phi_0)\left(|\nabla \phi| - 1\right) = 0$ (c.f. section \ref{section::levelset method}) \fcite{osher's book, smerka's paper?} or 2) Solving the static Eikonal equation $F(x)|\nabla\phi| = 1$ with constant speed function $F(x) \equiv 1$. The transient reinitialization equation can be solved using explicit finite differences and thus can easily be parallelized with a domain decomposition approach. Moreover, only a few iterations may be needed if the signed-distance property is only required close to the interface \fcite{Frederic's levelset paper}. This is the approach we have chosen in this paper. If, however, the signed-distance property is required in the entire domain solving the static Eikonal equation is more computationally efficient. Unfortunately, however, the most popular algorithm for solving the Eikonal equation, i.e. the Fast Marching Method \fcite{sethian's book, original FMM paper}, is inherently sequential due to causal relationship between grid points and cannot be easily parallelized. The Fast Sweeping Method (FSM) \fcite{Zhao's paper} is an alternative method for solving the static Eikonal equation iteratively which can be more computationally efficient for simple choices of speed function, e.g. as in this context, and for simple interfaces. Moreover, FSM has more potential for parallelization compared to the FMM.

\item \textbf{literature review on parallel levelset}
Large body of research has been devoted to parallelization of the level-set methods and here we review some of the more relevant works.
